---
title: "Homework7"
author: "Lizhuo Zhou 20307100132"
date: "05/14/2024"
output:
  pdf_document: default
  word_document: default
---

## Problem 1

```{r}
#Generate samples from N(1,4)
set.seed(35421)
data<-rnorm(100,mean=1,sd=2)
data
```

```{r}
estden.hist <- function(x,data,h){
  n <- length(data)
  range <- max(data)-min(data)
  block <- floor((x-min(data))/h)
  p.hat <- sum(data>=min(data)+range*(block-1)*h &
                 data<min(data)+range*block*h)/n
  return(p.hat/h)
}

```


```{r}

band.hcv<- function(data){
  h.candidate <- seq(from = 0.002, to = 0.7, by = 0.0001)
  n <- length(data)
  nh <- length(h.candidate)
  range <- max(data)-min(data)
  riskseq <- c()
  for (i in 1:nh){
    h <- h.candidate[i]
    p.hat = c()
    for (j in 1:n){
      p.hat[j] = sum(data>=min(data)+range*(j-1)*h
                     & data<min(data)+range*j*h)/n
    }
    
    # Empirical risk (6.16)
    riskseq[i] <- 2/h/(n-1)-(n+1)/h/(n-1)*sum(p.hat^2)
    }
  return(h.candidate[which.min(riskseq)])
  }


```

```{r}

estden.kernel <- function(x, data, h){
  n <- length(data)
  kernel.RBF <- function(x){exp(-(x^2)/2) / sqrt(2 * pi)}
  return(sum(kernel.RBF((x - data)/h)) / (n*h))
  }

```


```{r}
band.kcv<- function(data){
  h.candidate <- seq(from = 0.002, to = 0.7, by = 0.0001)
  n <- length(data)
  nh <- length(h.candidate)
  riskseq <- c()
  for (i in 1:nh){
    h <- h.candidate[i]
    # Integrated square estimation
    estdensq.kernel <- function(x){estden.kernel(x, data = data, h = h)^2}
    J1 <- integrate(Vectorize(estdensq.kernel),
                    lower = -1, upper = 2, subdivisions = 2000)$value
    # leave-one-out
    J2 <- 0
    for (j in 1:n){
      J2 <- J2 + estden.kernel(data[j], data = data[-j], h = h)
      }
    # Empirical risk (6.33)
    riskseq[i] <- J1 - (2 * J2)/n
    }
  return(h.candidate[which.min(riskseq)])
  }


```


```{r}

band.normal <-function(data){
  n <- length(data)
  s <- sd(data)
  qdata <- as.vector(quantile(data,probs=c(0.25,0.75)))
  Q <- qdata[2]-qdata[1]
  sigma <- min(s, Q/1.34)
  h <- 1.06*sigma*n^(-1/5)
  return(h)
  }


```




```{r}

# Density estimation
x.grid <- seq(from = -4.5, to = 7, by = 0.001)

# Histogram : Cross-Validation
h.hcv <- band.hcv(data)
y.grid_Hist <- sapply(x.grid, estden.hist, data = data, h = h.hcv)
plot(x.grid, y.grid_Hist, type = "l", xlab = "", ylab = "Density Estimate",
     main = "N(1,4): Histogrm density estimation with cross-validation")

# Kernel: Cross-Validation
h.kcv <- band.kcv(data)
y.grid_kernel <- sapply(x.grid, estden.kernel, data = data, h = h.kcv)
plot(x.grid, y.grid_kernel, type = "l", xlab = "", ylab = "Density Estimate",
     main = "N(1,4): Kernel density estimation with cross-validation")

# Kernel: Normal reference rule
h.normal <- band.normal(data)
y.grid_NRR <- sapply(x.grid, estden.kernel, data = data, h = h.normal)
plot(x.grid, y.grid_NRR, type = "l", xlab = "", ylab = "Density Estimate",
     main = "N(1,4): Kernel density estimation with normal reference rule")

# Density Function of N(1,4)
y.grid_denfunc <- sapply(x.grid,dnorm,mean=1,sd=2)
plot(x.grid, y.grid_denfunc, type = "l", xlab = "", ylab = "Density",
     main = "N(1,4):Density Function")


```

```{r}
#Combined Plot
plot(x.grid, y.grid_Hist, type = "l", xlab = "", ylab = "Density (Estimate)",
     main = "N(1,4) Sample Density(Estimate)")
lines(x.grid, y.grid_kernel,col="brown")
lines(x.grid, y.grid_NRR,col="blue")
lines(x.grid, y.grid_denfunc,col="orange")


```

```{r}
#The built-in function

plot(density(data),main="Density by the built-in function")


```



\
\ \ Conclusion:
\
\ \ I have plotted a density function of N(1,4), a histogram density estimator, a kernel density estimator, both with cross-validation; and a kernel density estimator with normal reference rule. Eventually, the comparison of the 4 curves are drawn in the same plot.
\
\ \ The bandwidth that the built-in function use is 0.6028.









\
\ \ Conclusion: The corresponding p-value is 0.464 > 0.1 and we fail to reject the null.


