---
title: "Homework 2"
author: "Lizhuo Zhou 20307100132"
date: "03/21/2024"
output:
  pdf_document: default
  word_document: default
---

## Problem 1
\ 

```{r} 
# D: Kolomogorov-Smirnov One-Sample Statistic
# n: the number of samples
# nrep: the number of samples for simulation
ks_pvalue<-function(D,n,nrep){
Dn <- c()
for (i in 1:nrep) {
x.obs <- rnorm(n,0,1)
Fn.hat <- ecdf(x.obs)
Dn[i] <- max(abs(Fn.hat(x.obs) - pnorm(x.obs)))
}
return(sum(Dn > D)/nrep)
}


```


```{r}
# Calculate the p-value of the statistics under the problem setting

D = 0.05; n = 100; nrep = 5000
ks_pvalue(D,n,nrep)

```

\
\ \ Conclusion: The result shows that the p-value is 0.91>0.05, so that we fail to reject the null hypothesis at level $\alpha=0.05$.


## Problem 2
\ 

```{r}
set.seed(2)
d<-rcauchy(50)

emp.inv<-sort(d)
sel<-seq(1,50,by=1)/50
norm.inv<-qnorm(sel)
plot(norm.inv,emp.inv)

abline(0,1,col='red')
```
\
\ \ Conclusion:
\
\ \ From above, we could see that the simulation of Cauchy distribution does not perfectly fit a normal distribution. Only the middle part of the plot relatively fits the normal distribution, but the plot's head and tail are far from normally distributed, indicating the simulated data's kurtosis exceeds that of a standard normal distribution.


## Problem 3
\ 

```{r} 
wilcox.stats <- function(x, med){
  s <- sign(x-med)
  s.abs <- abs(x-med)
  return(sum(rank(s.abs)[s>0])-sum(rank(s.abs)[s<0]))
}

```

```{r} 
wilcox.pvalue <- function(x, med, nrep){
  stats <- wilcox.stats(x, med)
  record <- c()
  for (i in 1:nrep){
    record[i] <- wilcox.stats(rnorm(20), 0)
  }
  
  # Calculate the two-sided p-value
  return(2*min(mean(record < stats), mean(record > stats)))}

```

```{r}
# Calculate the p-value of the statistics under the problem setting
set.seed(20355)
x <- rnorm(20,mean=0,sd=1); med <- 0.1; nrep <- 50000
wilcox.pvalue(x, med, nrep)

```

\
\ \ Conclusion:
\
\ \ The corresponding p-value is 0.59152>0.05, and we fail to reject the null at level 0.05.









