---
title: "Homework 5"
author: "Lizhuo Zhou 20307100132"
date: "04/10/2024"
output:
  pdf_document: default
  word_document: default
---

## Problem 1
\ 
```{r 1} 
corr.Kendall<-function(x,y){
  n = length(x)
  x.sign = apply(matrix(x,nrow = 1), MARGIN = 2,function(data){sign(x-data)})
  y.sign = apply(matrix(y,nrow = 1), MARGIN = 2,function(data){sign(y-data)})
  tau = (sum(x.sign*y.sign)/2)/choose(n,2)
  return(tau)
}

corr.Spearman<-function(x,y){
  x.rank = rank(x); y.rank = rank(y)
  return(cor(x.rank,y.rank))
}


corr.pvalue <- function(x,y,nrep){
  n <- length(x)
  # Calculate the test statistics
  stats.Kendall <- corr.Kendall(x, y)
  stats.Spearman <- corr.Spearman(x, y)
  # Simulate under the null
  sim.Kendall <- c(); sim.Spearman <- c()
  for (i in 1:nrep) {
    sim.1 <- rnorm(n,0,1); sim.2 <- rnorm(n,0,1);
    sim.Kendall[i] <- corr.Kendall(sim.1,sim.2)
    sim.Spearman[i] <- corr.Spearman(sim.1,sim.2)
    }
  return(list(Kendall=2*min(mean(sim.Kendall<stats.Kendall),
                            mean(sim.Kendall>stats.Kendall)),
              Spearman=2*min(mean(sim.Spearman<stats.Spearman),
                             mean(sim.Spearman>stats.Spearman))))
  }


```


```{r 2}

# Calculate the p-value of the statistics under the problem setting
set.seed(258)
X = runif(50,-1,1); Y = rnorm(50,sqrt(1-X^2),1); nrep = 500
corr.pvalue(X,Y,nrep)

```
\
\ \ Conclusion:
\
\ \ Both of the test failed to reject the null under the problem setting with respectively p-value of 0.164 and 0.196. Kendall's and Spearman's correlation test both fail to reject the null with level $\alpha=0.05$.

## Problem 2

```{r 3}
 corr.power <- function(np,nrep){
   power.Kendall <- 0; power.Spearman <- 0;
   for (i in 1:np){
     X = runif(10,1,2); Y = rnorm(10,X/2,0.1)
     pvalue <- corr.pvalue(X,Y,nrep)
     power.Kendall <- power.Kendall+ ifelse(pvalue$Kendall<0.05,1,0)
     power.Spearman <- power.Spearman+ ifelse(pvalue$Spearman<0.05,1,0)
     print(pvalue)
     }
   return(list(Kendall=power.Kendall/np,Spearman=power.Spearman/np))
   }


```

```{r 4}
corr.power(200,1000)
```
\
\ \ Conclusion:
\
\ \ The estimated power of Kendall’s and Spearman’s correlation test is approximately 0.04 and 0.07
under the problem setting and the latter one is more powerful.



### Problem 3

\
\ \ Analysis:
\
\ \ Use the extension of the median test, where the test statistic is $\dfrac{N(N-1)Q}{N},Q=\dfrac{N^2}{t(N-t)}\sum_{i=1}^{k}\dfrac{(u_{i}-n_{i}t/N)^2}{n_{i}}$.
\
\ \ The null hypothesis would be equal medians for the three groups(Drug A,B, and C).


```{r 5}
extend.median.Q <- function(x,y,z){
  sample_matrix<-cbind(x,y,z)
  N<-ncol(sample_matrix)*nrow(sample_matrix)
  t<-N/2
  sample_median<-median(sample_matrix)
  compare_matrix<-matrix(0,2,ncol(sample_matrix))
  compare_matrix[1,1]<-sum(table(sample_matrix[,1])[sample_matrix[,1]<sample_median])
  compare_matrix[2,1]<-nrow(sample_matrix)-compare_matrix[1,1]
  compare_matrix[1,2]<-sum(table(sample_matrix[,2])[sample_matrix[,2]<sample_median])
  compare_matrix[2,2]<-nrow(sample_matrix)-compare_matrix[1,2]
  compare_matrix[1,3]<-sum(table(sample_matrix[,3])[sample_matrix[,3]<sample_median])
  compare_matrix[2,3]<-nrow(sample_matrix)-compare_matrix[1,3]
  Q<-0
  for (i in 1:ncol(sample_matrix)){
    Q<-Q+(compare_matrix[1,i]-nrow(sample_matrix)*t/N)^2/nrow(sample_matrix)
  }
  
  return(((N-1)/N)*(N^2/((N-t)*t))*Q)
  
}

```



```{r 6}
#Under problem setting



A<-c(10.2,10.5,11.8,8.7,7.5,15.3)
B<-c(9.8,14.2,15.1,12.3,11.8,10.5)
C<-c(13.6,19.7,11.1,10.8,9.2,14.9)

pchisq(extend.median.Q(A,B,C),df=2)
```

\
\ \ Conclusion:
\
\ \ Since 0.467>0.05, there is no evidence that the three medians differ at level $\alpha=0.05$.
\
\ \  That is, these data don't provide sufficient evidence to indicate that the three drugs differ in their effects at level $\alpha$= 0.05.




